### 2018-03-12 paper/3-compute.tex
Expand the Indentity monad construction

\noindent
Since the first argument is polymorphic in \hs{f}, we can choose any \hs{f} that
satisfies the \hs{Applicative} constraint. A good choice in this case is the
applicative functor \hs{Const} defined in GHC's standard library module
\cmd{Data.Functor.Const}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Const m a = Const { getConst :: m }

instance Functor (Const m) where
    fmap _ (Const m) = Const m

instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{1mm}

@@

We can also execute a compute on a given store. This relies on a similar
transformation, now based on the \hs{Identity} monad defined in
\cmd{Data.Functor.Identity}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
execute :: Compute Monad k v -> (k -> v) -> k -> Maybe v
execute compute store = fmap runIdentity . compute (Identity . store)
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ store key = if key == "A1" then 10 else 20
@\ghci@ execute add store "A1"
Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ execute add store "B1"
Just 30
\end{minted}
\vspace{1mm}

>>>>

\noindent
Since the first argument is polymorphic in \hs{f}, we can choose any \hs{f} that
satisfies the \hs{Applicative} constraint. A good choice in this case is the
applicative functor \hs{Const}:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Const m a = Const { getConst :: m }
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor (Const m) where
    fmap _ (Const m) = Const m
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monoid m => Applicative (Const m) where
    pure _              = Const mempty
    Const x <*> Const y = Const (x <> y)
\end{minted}
\vspace{1mm}

@@

We can also \hs{execute} a compute on a given store. This relies on a similar
transformation, now based on the \hs{Identity} monad and feeding
\hs{fetch k = pure (store k)} to the compute:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
execute :: Compute Monad k v -> (k -> v) -> k -> Maybe v
execute compute store = fmap runIdentity . compute (pure . store)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
newtype Identity a = Identity { runIdentity :: a }
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Functor Identity where
    fmap f (Identity a) = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Applicative Identity where
    pure a = Identity a
    Identity f <*> Identity a = Identity (f a)
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
instance Monad Identity where
    Identity a >>= f = f a
\end{minted}
\vspace{1mm}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ store key = if key == "A1" then 10 else 20
@\ghci@ execute add store "A1"
Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ execute add store "B1"
Just 30
\end{minted}
% \vspace{1mm}
